The Fermi surface and competition between superconductivity and charge density wave

### 2018-08-14 2018_08_13/paper.tex
update

>>>>

\begin{frame}{Implications for the phase diagrams}
\begin{itemize}
\item A Landau theory: $T_c$ is suppressed in the presence the CDW
\item $T_{\text{CDW}}$ corresponds with $T_\text{H}$, where Hall effect measurements suggest FS reconstruction
\item A CDW that breaks translational symmetry explains the mechanism of FS reconstruction
\end{itemize}
\begin{figure}
\includegraphics[width=1.5in]{figs/chang_4.pdf}
\caption{\label{fig:chang_4} Doping dependence of several ordering temperatures}
\end{figure}
\end{frame}
